---
title: "Business Understanding"
author: "Manmeet Bains"
date: "9/27/2019"
output: rmarkdown::github_document
---

```{r}
#Libraries
library(tidyverse)
library(tidyquant)
library(readxl)
library(forcats)
library(stringr)

```

```{r}
# Load Data
Path_train <- "00_Data/telco_train.xlsx"

train_raw_data <- read_excel(Path_train, sheet = 1)
```

```{r}
# Subset Data

dept_job_role_tbl <- train_raw_data %>%
  select(EmployeeNumber, Department, JobRole, PerformanceRating, Attrition)
```

# 1. Business Science Problem Framework ----

# 1A. View Business As Machine ----

# BSU's: Department and Job Role
# Define Objectives: Retrain High Performers
# Assess Outcomes: TBD 

```{r}
dept_job_role_tbl %>% 
  group_by(Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(pct = n / sum(n))
```

# 1B. Understand The Drivers ----

# Investigate Objectives: 16% Pct Attrition
# Sythesize Outcomes: High Counts and High percentages 
# Hypothesize Drivers: Job Role and Departments

```{r}
# Department ----
dept_job_role_tbl %>% 
  
  group_by(Department, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  
  group_by(Department) %>%
  mutate(pct = n / sum(n))
```


```{r}
# Job Role ----
dept_job_role_tbl %>% 
  
  group_by(Department, JobRole, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  
  group_by(Department, JobRole) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup() %>%
  
  filter(Attrition %in% c("Yes"))
```


# 1C. Measure The Drivers ----

# Collect Information on Employee Attrition: On going

# Develop KPI's: Industry KPIs: 8.8%

```{r}
dept_job_role_tbl %>% 
  
  group_by(Department, JobRole, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  
  group_by(Department, JobRole) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup() %>%
  
  filter(Attrition %in% c("Yes")) %>%
  arrange(desc(pct)) %>%
  mutate(
    above_industry_avg = case_when(
      pct > 0.088 ~ "Yes",
      TRUE ~ "No"
    )
  )
```

```{r}
# 1D. Uncover Problems and Opportunities ----

calculate_attrition_cost <- function(
  
  # Employee
  n                    = 1,
  salary               = 80000,
  
  # Direct Costs
  separation_cost      = 500,
  vacancy_cost         = 10000,
  acquisition_cost     = 4900,
  placement_cost       = 3500,
  
  # Productivity Costs
  net_revenue_per_employee = 250000,
  workdays_per_year        = 240,
  workdays_position_open   = 40,
  workdays_onboarding      = 60,
  onboarding_efficiency    = 0.50
  
) {
  
  # Direct Costs
  direct_cost <- sum(separation_cost, vacancy_cost, acquisition_cost, placement_cost)
  
  # Lost Productivity Costs
  productivity_cost <- net_revenue_per_employee / workdays_per_year * 
    (workdays_position_open + workdays_onboarding * onboarding_efficiency) 
  
  # Savings of Salary & Benefits (Cost Reduction)
  salary_benefit_reduction <- salary / workdays_per_year * workdays_position_open
  
  # Estimated Turnover Per Employee
  cost_per_employee <- direct_cost + productivity_cost - salary_benefit_reduction
  
  # Total Cost of Employee Turnover
  total_cost <- n * cost_per_employee
  
  return(total_cost)
  
}

```


```{r}
# Calculate Cost By Job Role ---- 

dept_job_role_tbl %>% 
  
  group_by(Department, JobRole, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  
  group_by(Department, JobRole) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup() %>%
  
  filter(Attrition %in% c("Yes")) %>%
  arrange(desc(pct)) %>%
  mutate(
    above_industry_avg = case_when(
      pct > 0.088 ~ "Yes",
      TRUE ~ "No"
    )
  ) %>%
  
  mutate(
    cost_of_attrition = calculate_attrition_cost(n = n, salary = 80000)
  )

```

























